Predictive modeling with cross validation

### 2017-08-12 model fitting/cross_validation.Rmd
plotted residuals, updated hours

# if there are less than 60 questions in a category, group them with other
counts <- train1 %>%
  group_by(new_category) %>%
  summarise(n = n())
for (i in which(counts$n <= 100)) {
  train1$new_category[train1$new_category == counts$new_category[i]] <- "Other"
}

table(train1$new_category)

@@

>>>>

# if there are less than 60 questions in a category, group them with other
counts <- train1 %>%
  group_by(new_category) %>%
  summarise(n = n())
for (i in which(counts$n <= 100)) {
  train1$new_category[train1$new_category == counts$new_category[i]] <- "Other"
}
table(train1$new_category)
#===================================================

@@

### residuals, PH assumption

```{r}
#=============================================
#martingale residuals
train1$mart <- residuals(r2_new, type = "martingale")

plot_res <- function(var, residuals, data, title) {
  ggplot(data, aes(x = data[[var]], y = residuals)) +
    geom_point() +
    geom_smooth() + 
    ggtitle(title) + 
    scale_x_continuous(var)
}

res_image <- plot_res(var = "n_images", residuals = mart, data = train1, title = "Martingale Residuals for n_images")
res_dev <- plot_res("device_length", mart, data = train1, title = "Martingale Residuals for device_length")
res_newline <- plot_res("newline_ratio", mart, data = train1, title = "Martingale Residuals for newline_ratio")

gridExtra::grid.arrange(res_image, res_dev, res_newline, nrow=1, ncol=3)

#=============================================
#deviance residuals 
train1$deviance <- residuals(r2_new, type = "deviance")
ggplot(train1, aes(x = 1:nrow(train1), y = deviance)) + 
  geom_point() + 
  scale_x_continuous("Question index") + 
  scale_y_continuous(breaks = seq(-4, 4, by = 0.5))
# quite a few questions have a deviance residual of larger than 2.5

#=============================================
#schoenfeld residuals
schoen <- as.data.frame(residuals(r2_new, type = "schoenfeld"))
# complete event times sorted from shortest to longest
schoen$comp_times <- sort(train1[train1$answered != 0,]$time_until_answer)

plot_schoen <- function(var) {
  ggplot(schoen, aes(x = comp_times, y = schoen[[var]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Schoenfeld Residuals for", var)) + 
    scale_y_continuous("Residuals")
}
names <- names(schoen)[-31]
purrr::map(names, plot_schoen)

#=============================================
# score residuals
score <- as.data.frame(residuals(r2_new, type = "score"))
# function to plot score residuals
plot_score <- function(column) {
  ggplot(score, aes(x = 1:nrow(score), y = score[[column]])) + 
    geom_point() + 
    geom_smooth() + 
    ggtitle(paste("Score residuals for", column)) + 
    scale_y_continuous("Score Residuals") + 
    scale_x_continuous("Question index")
}
columns <- names(score)
purrr::map(columns, plot_score)
```

### Predicting on the test data

```{r}
test1 <- x[splitPlan[[1]]$app, ]
# predict.coxph
```
